\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex
Fix name
add up/download figs
eval section

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Dark Decoys:
  Conjuring Proxies from Unused Address Space}
\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}

@@

\newcommand{\scheme}{Conjure\xspace}
%\newcommand{\scheme}{Dark Decoys\xspace}

@@

\TODO{Write (1 page)}

Compare to TapDance performance:
-Connection setup time
-Connection/session lifetime
-Throughput (especially upload vs download)
-Security considerations

>>>>

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Dark Decoys:
  Conjuring Proxies from Unused Address Space}
%\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}

@@

%\newcommand{\scheme}{Conjure\xspace}
\newcommand{\scheme}{Dark Decoys\xspace}

@@

%\TODO{Write (1 page)}

\FigTapBandwidth

\FigUpload

\FigDownload

To evaluate our \scheme implementation, we compare its bandwidth
to that of TapDance in a realistic ISP setting. We used a full duplex 10~Gbps
network tap at a mid-sized ISP and run both implementations on a 1U server with
an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
network interface. A typical week of bandwidth seen on the tap is
shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
17~Gbps.

We evaluated the performance of a client from a Singapore-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation, and a direct
connection to our iperf server in the ISP's network.

TapDance must reconnect if the amount of data sent by the client
exceeds a short TCP window (typically on the order of 32~KBytes) or the
connection persists until a timeout (18-120 seconds). At each reconnect, the
TapDance client naively blocks until a new TLS connection to the decoy and
station has been established. Thus, when uploading files, TapDance has to create
a new TLS connection for every 32~KBytes of data it sends, limiting its average
upload bandwidth to less than 1~Mbps due to the high overhead. In contrast,
our \scheme implementation is
able to maintain the same connection during large uploads, and achieves
performance inline with the direct connection.

During download-only workloads, TapDance is able to better utilize the network,
but must still reconnect before the decoy times out. In our tests, we see
TapDance reconnect every 25 seconds, which can negatively impact the performance of
downloads or any real-time streaming applications. Again, our \scheme
implementation is able to maintain a single connection and provide the maximum
download rate without interruption.

%Compare to TapDance performance:
%-Connection setup time
%-Connection/session lifetime
%-Throughput (especially upload vs download)
%-Security considerations
